### 2016-09-22 oldmort.Rnw
fix file names, more remains
make working

\usepackage[tablesonly]{endfloat}
\usepackage{endfloat}

@@

The {\sc Lisa} data is yearly, with {\tt hisclass} information starting in 2002. This information, however, do not allow us to contemplate seven (or six) levels, so we are using only four classes, grouping together 1+2, 3+4, and 5 + 6.

@@

<<readtab>>=
load("vbTab.rda")
@

@@

<<colorc>>=
## Colors for plotting strata:
scol <- c("blue", rep("green", 2), "red")
## Common for all groups:

@@

%The distribution over time periods.
<<getske4060>>=
cap1w <-  "Cumulative hazards for HISCLASS by time period, ages 40--59, women."
scap1w <-  "Cumulative hazards, ages 40--59, women."
cap1m <-  "Cumulative hazards for HISCLASS by time period, ages 40--59, men."
scap1m <-  "Cumulative hazards, ages 40--59, men."
##
cap12 <- "Total hazard of dying before age 60 for a 40 year old person by HISCLASS and decade, women (top) and men (bottom)."
scap12 <- "Total hazard by HISCLASS, ages 40--59."    
cap12log <- "Total hazard of dying before age 60 for a 40 year old person by HISCLASS and decade, women (top) and men (bottom). Log scale."
scap12log <- "Total hazard by HISCLASS, ages 40--59 (log scale)."

cap2w <-  "Cumulative hazards for HISCLASS by time period, ages 60--89, women."
scap2w <-  "Cumulative hazards, ages 60--89, women."
cap2m <-  "Cumulative hazards for HISCLASS by time period, ages 60--89, men."
scap2m <-  "Cumulative hazards, ages 60--89, men."
##
cap22 <- "Total hazard of dying before age 90 for a 60 year old person by HISCLASS and decade, women (top) and men (bottom)."
scap22 <- "Total hazard by HISCLASS, ages 60--89."

@@

<<hazplotw, fig.cap = cap1w, fig.scap = scap1w, fig.height = 10>>=
source("R/plotHaz.glm.R")
plotHaz.glm(resw, main = labb)
@

<<hazplotm, fig.cap = cap1m, fig.scap = scap1m, fig.height = 10>>=
plotHaz.glm(resm, main = labb)
@

@@

<<cumsw, fig.cap = cap12, fig.scap = scap12, fig.height = 10>>=
source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1))
woutp <- plotED.glm(resw, scol = scol, logScale = FALSE, ylab = "H(60|40)",
                main = "Women")
moutp <- plotED.glm(resm, scol = scol, logScale = FALSE, ylab = "H(60|40)",
                main = "Men")
par(oldpar)
@

@@

<<cumslogw, fig.cap = cap12log, fig.scap = scap12log, fig.height = 10>>=
oldpar <- par(mfrow = c(2, 1))
wloutp <- plotED.glm(resw, scol = scol, logScale = TRUE, ylab = "H(60|40)",
main = "Women")
mloutp <- plotED.glm(resm, scol = scol, logScale = TRUE, ylab = "H(60|40)",
main = "Men")
par(oldpar)
@

@@

<<lissyoung>>=
liss4059 <- age.window(liss, c(40, 59))
@

<<liswom>>=
fitw1 <- phreg(Surv(enter-40, exit-40, event) ~ strata(hisclass) + civst + urban, dist = "gompertz", data = liss4059[liss4059$sex == "female", ])
fitm1 <- phreg(Surv(enter-40, exit-40, event) ~ strata(hisclass) + civst + urban, dist = "gompertz", data = liss4059[liss4059$sex == "male", ])
dcol <- c("blue", "darkgreen", "darkgreen", "red")
@

@@

See Table~\ref{tab:tablisswom1} the PH regression for women.
<<tablisswom1, results = "asis">>=
fitwo1 <- coxreg(Surv(enter, exit, event) ~ hisclass + civst + urban + period, 
                 data = liss4059[liss4059$sex == "female", ])
dr <- drop1(fitwo1, test = "Chisq")
ltx(fitwo1, dr = dr, caption = "PH regression, women aged 40--59, 2002--2013.", 
    label = "tab:tablisswom1")
@

See Table~\ref{tab:tablissman1} the PH regression for men.
<<tablissman1, results = "asis">>=
fitma1 <- coxreg(Surv(enter, exit, event) ~ hisclass + civst + urban + period, 
                 data = liss4059[liss4059$sex == "male", ])
dr <- drop1(fitma1, test = "Chisq")
ltx(fitma1, dr = dr, caption = "PH regression, men aged 40--59, 2002--2013.", 
    label = "tab:tablissman1")
@

@@

<<hazcalwold>>=
resw <- getPH(vb6089[vb6089$sex == "female", ],
              nper, labb)
resm <- getPH(vb60896089[vb6089$sex == "male", ],
                nper, labb)
@

<<hazplotwold, fig.cap = cap2w, fig.scap = scap2w, fig.height = 10>>=
##source("R/plotHaz.R")
plotHaz.glm(resw, main = labb)
@

<<hazplotmold, fig.cap = cap2w, fig.scap = scap2m, fig.height = 10>>=
plotHaz.glm(resm, main = labb)
@

@@

<<cumswold, fig.cap = cap22, fig.scap = scap22, fig.height = 10>>=
##source("R/plotED.R")
oldpar <- par(mfrow = c(2, 1))
woutp <- plotED.glm(resw, scol = scol, logScale = FALSE, ylab = "H(90|60)",
                main = "Women")
moutp <- plotED.glm(resm, scol = scol, logScale = FALSE, ylab = "H(90|60)",
                main = "Men")
par(oldpar)
@

@@

%% <<cumslogwold, fig.cap = "Probability of dying before age 90 for a 60 year old person by HISCLASS and decade, log scale, women (top) and men (bottom).", fig.height = 10>>=
%% oldpar <- par(mfrow = c(2, 1))
%% wloutp <- plotED.ph(resw, scol = scol, logScale = TRUE, ylab = "H(60|40)",
%% main = "Women")
%% mloutp <- plotED.ph(resm, scol = scol, logScale = TRUE, ylab = "H(60|40)",
%% main = "Men")
%% par(oldpar)
%% @

>>>>

%\usepackage[tablesonly]{endfloat}
\usepackage{endfloat}

@@

The {\sc Lisa} data is yearly, with {\tt hisclass} information starting in 2002. This information, however, do not allow us to contemplate seven (or six) levels, so we are using only four classes, grouping together 1+2, 3+4, 5, and 6.

@@

<<readtab>>=
load("../CreateData/data4/vbTab.rda")
@

@@

<<colorc>>=
## Colors for plotting strata:
scol <- c("blue", rep("darkgreen", 2), "red")
## Common for all groups:

@@

%The distribution over time periods.
<<getske4060>>=
cap1w <-  "Cumulative hazards for HISCLASS by time period, ages 40--59, women."
scap1w <-  "Cumulative hazards, ages 40--59, women."
cap1m <-  "Cumulative hazards for HISCLASS by time period, ages 40--59, men."
scap1m <-  "Cumulative hazards, ages 40--59, men."
##
cap12 <- "Total hazard of dying before age 60 for a 40 year old person by HISCLASS and decade, women (top) and men (bottom)."
scap12 <- "Total hazard by HISCLASS, ages 40--59."    
cap12log <- "Total hazard of dying before age 60 for a 40 year old person by HISCLASS and decade, women (top) and men (bottom). The last decades."
scap12log <- "Total hazard by HISCLASS, ages 40--59, last years."

cap2w <-  "Cumulative hazards for HISCLASS by time period, ages 60--89, women."
scap2w <-  "Cumulative hazards, ages 60--89, women."
cap2m <-  "Cumulative hazards for HISCLASS by time period, ages 60--89, men."
scap2m <-  "Cumulative hazards, ages 60--89, men."
##
cap22 <- "Total hazard of dying before age 90 for a 60 year old person by HISCLASS and decade, women (top) and men (bottom)."
scap22 <- "Total hazard by HISCLASS, ages 60--89."    
cap22log <- "Total hazard of dying before age 90 for a 60 year old person by HISCLASS and decade, women (top) and men (bottom). The last decades."
scap22log <- "Total hazard by HISCLASS, ages 60--89, last years."

@@

<<hazplotw, fig.cap = cap1w, fig.scap = scap1w, fig.height = 7>>=
source("R/plotHaz.glm.R")
plotHaz.glm(resw[-(1:6)], main = labb, col = scol, layout = c(2, 2))
@

<<hazplotm, fig.cap = cap1m, fig.scap = scap1m, fig.height = 7>>=
plotHaz.glm(resm[-(1:6)], main = labb, col = scol, layout = c(2, 2))
@

@@

<<cumsw, fig.cap = cap12, fig.scap = scap12, fig.height = 10>>=
source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1))
woutp <- plotED.glm(resw, col = scol, logScale = FALSE, ylab = "H(60|40)",
                main = "Women")
moutp <- plotED.glm(resm, col = scol, logScale = FALSE, ylab = "H(60|40)",
                main = "Men")
par(oldpar)
@

@@

In Figure~\ref{fig:cumslogw} a "blow-up" of the last decades show clearly the upper hand of the upper classes.

<<cumslogw, fig.cap = cap12log, fig.scap = scap12log, fig.height = 10>>=
oldpar <- par(mfrow = c(2, 1))
wloutp <- plotED.glm(resw[-(1:6)], col = scol, logScale = FALSE, ylab = "H(60|40)",
main = "Women")
mloutp <- plotED.glm(resm[-(1:6)], col = scol, logScale = FALSE, ylab = "H(60|40)",
main = "Men")
par(oldpar)
@

@@

<<lissyoung>>=
load("../CreateData/data4/liss.rda")
liss4059 <- age.window(liss, c(40, 59))
@

<<liswom, cache = TRUE>>=
fitw1 <- phreg(Surv(enter-40, exit-40, event) ~ strata(hisclass) + civst + urban, dist = "gompertz", data = liss4059[liss4059$sex == "female", ])
fitm1 <- phreg(Surv(enter-40, exit-40, event) ~ strata(hisclass) + civst + urban, dist = "gompertz", data = liss4059[liss4059$sex == "male", ])
dcol <- c("blue", "darkgreen", "darkgreen", "red")
@

@@

See Table~\ref{tab:tablisswom1} the PH regression for women.
<<tablisswom1, results = "asis", cache = TRUE>>=
fitwo1 <- coxreg(Surv(enter, exit, event) ~ factor(hisclass) + civst + urban + period, 
                 data = liss4059[liss4059$sex == "female", ])
dr <- drop1(fitwo1, test = "Chisq")
ltx(fitwo1, dr = dr, caption = "PH regression, women aged 40--59, 2002--2013.", 
    label = "tab:tablisswom1")
@

See Table~\ref{tab:tablissman1} the PH regression for men.
<<tablissman1, results = "asis", cache = TRUE>>=
fitma1 <- coxreg(Surv(enter, exit, event) ~ factor(hisclass) + civst + urban + period, 
                 data = liss4059[liss4059$sex == "male", ])
dr <- drop1(fitma1, test = "Chisq")
ltx(fitma1, dr = dr, caption = "PH regression, men aged 40--59, 2002--2013.", 
    label = "tab:tablissman1")
@

@@

<<hazcalwold>>=
resw <- getPHglm(vb6089[vb6089$sex == "female", ],
              nper, labb)
resm <- getPHglm(vb6089[vb6089$sex == "male", ],
                nper, labb)
@

<<hazplotwold, fig.cap = cap2w, fig.scap = scap2w, fig.height = 7>>=
##source("R/plotHaz.R")
plotHaz.glm(resw[-(1:6)], main = labb, layout = c(2, 2), col = scol)
@

<<hazplotmold, fig.cap = cap2w, fig.scap = scap2m, fig.height = 7>>=
plotHaz.glm(resm[-(1:6)], main = labb, layout = c(2, 2), col = scol)
@

@@

<<cumswold, fig.cap = cap22, fig.scap = scap22, fig.height = 10>>=
##source("R/plotED.R")
oldpar <- par(mfrow = c(2, 1))
woutp <- plotED.glm(resw, col = scol, logScale = FALSE, ylab = "H(90|60)",
                main = "Women")
moutp <- plotED.glm(resm, col = scol, logScale = FALSE, ylab = "H(90|60)",
                main = "Men")
par(oldpar)
@

A blow-up of the last years is shown in Figure~\ref{fig:cumslogwm}.

<<cumslogwm, fig.cap = cap22log, fig.scap = scap22log, fig.height = 10>>=
oldpar <- par(mfrow = c(2, 1))
wloutp <- plotED.glm(resw[-(1:6)], col = scol, logScale = FALSE, ylab = "H(90|60)",
main = "Women")
mloutp <- plotED.glm(resm[-(1:6)], col = scol, logScale = FALSE, ylab = "H(90|60)",
main = "Men")
par(oldpar)
@

@@

%% <<cumslogwold, fig.cap = "Probability of dying before age 90 for a 60 year old person by HISCLASS and decade, log scale, women (top) and men (bottom).", fig.height = 10>>=
%% oldpar <- par(mfrow = c(2, 1))
%% wloutp <- plotED.ph(resw, col = scol, logScale = TRUE, ylab = "H(60|40)",
%% main = "Women")
%% mloutp <- plotED.ph(resm, col = scol, logScale = TRUE, ylab = "H(60|40)",
%% main = "Men")
%% par(oldpar)
%% @
